A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
spellers and typos

We evaluate our approaches in robot exploration tasks from home and
office environments. Spatially, these consist of {\em rooms}
(office/kitchen/etc), and an underlying topological map that models
smaller areas of space, called {\em places}, and connectivity between
those. The mobile {\em robot} and {\em visual objects} inhabit the
topological space, the latter indicate the category of space they
inhabit -- e.g., Spoons are likely to be in kitchens. By examining
view cones at places for particular objects, the robot is able to: (1)
categorise space at high (room) and low (place) levels, and (2) find
objects for the user, exploiting information about object
co-occurrence and room categories for efficiency. Also, in the
presence of a person, the robot can ask them about the location of
objects.

>>>>

We evaluate our approaches in robot exploration tasks from home and
office environments. Spatially, these consist of {\em rooms}
(office/kitchen/etc), and an underlying topological map that models
smaller areas of space, called {\em places}, and connectivity between
those. The mobile {\em robot} and {\em visual objects} inhabit the
topological space, the latter indicate the category of space they
inhabit -- e.g., spoons are likely to be in kitchens. By examining
view cones at places for particular objects, the robot is able to: (1)
categorise space at high (room) and low (place) levels, and (2) find
objects for the user, exploiting information about object
co-occurrence and room categories for efficiency. Also, in the
presence of a person, the robot can ask them about the location of
objects.
